%1-lep DNN ML
\clearpage
\section{Conclusions}

This thesis has presented a search for semileptonic Vector Boson Scattering (VBS) events, utilizing the complete Run-II dataset collected by the ATLAS detector at the LHC. Significant emphasis was placed on my contributions, particularly on the deployment of a Deep Neural Network (DNN) approach to analyze and enhance sensitivity to the SM VBS signal in the \olep channel.

The preliminary unblinded results from this study have shown an observed significance of $5.78\sigma$, which exceeds the critical $5\sigma$ observation threshold, with a reported signal strength parameter $\mu_{VBS} = 1.16 \pm 0.25$. This achievement is notable as it suggests the feasibility of observing VBS events through the analysis of the \olep channel alone.

The DNN methodology introduced here serves as an alternative machine learning strategy within the broader context of a combined search~\cite{Charlton:2808769} across three channels (\zlep, \olep, and \tlep), which utilized a Recurrent Neural Network (RNN) approach. While a direct comparison between the DNN and RNN methods does not definitively establish one as superior to the other, it can be argued, based on this work, that the simpler yet effective DNN approach may offer a more suitable solution for future analyses.
The significance of this work lies in its demonstration of the DNN’s potential to enhance the analysis of semileptonic VBS events. By achieving significant results in the 1-lepton channel, this research contributes to the evolving understanding of VBS processes and their observation at the LHC.

This research encountered several limitations, partly due to the extended duration of the combined search across the three channels. This period coincided with unforeseen challenges posed by the COVID-19 pandemic, which indirectly affected the scope of the investigation.
This thesis did not account for signal uncertainties arising from EWK-QCD interference and parton shower systematics. More comprehensive studies of the nuisance parameters and adjustments in the binning strategies for certain NPs could potentially improve the fit results and overall analysis sensitivity.

The study of anomalous quartic gauge couplings (aQGC) is a significant yet ongoing aspect of the combined search, briefly discussed in this thesis. While my involvement in this specific area was limited, the potential for investigating aQGCs exclusively within the \olep channel—especially with additional data from the ATLAS detector—presents an intriguing avenue for future research.

Addressing these limitations presents an opportunity for subsequent research to build upon the foundational work laid out in this thesis, thereby further advancing our understanding and analysis capabilities in the field of semileptonic VBS analysis.

