%%% EventSelection %%%

This section describes the event selection, which has been optimized in order to maximize the expected significance of the signal over background.

A set of preselection cuts are applied first, including basic quality cuts (event cleaning) and  trigger requirements.
Some preselection cuts applied in the \texttt{CxAODMaker} are also summarized.

For the main event selection, first the selection of the $W/Z$ boson decaying leptonically is performed. 
The candidate boson is selected targeting $Z\to \ell\ell$, $W\to \ell\nu$ and $Z\to \nu\nu$, respectively.

Then in each lepton channel, the hadronic part of the final state is considered 
in order to enhance the VBS associated objects and to select the second boson decaying hadronically. 
A usual tagging jets procedure is performed for the VBS-jet candidates selection 
while a hadronically decaying $V$ candidate is identified, 
either reconstructed as a large-$R$ jet (merged regime), or two small-$R$ jets (resolved regime).

In each channel, some topological cuts are applied to suppress the background. 
Cuts are designed to define some analysis SRs, with enhanced sensitivity to the target signal,
and some analysis CRs, with enhanced SM background processes to constraint them in the fit. 
In particular, for events falling in the merged regime the boson tagger is used to define the SRs 
and reverted cut for defining CRs for the \Vjets background; for events in the resolved regime,
a signal di-jets system is built and the invariant mass of it is used to define a mass window (SR) 
or sidebands (CRs for \Vjets). Only in the \olep channel, dedicated TopCR are defined r
equiring additional b-jets in the event.

%The current selection is mainly reproducing what has been optmised in the previous round, 
%except for some dedicated optimisations:

First a summary of all the selections will be provided to give an full overview of it to the reader,
then, the detailed selections will be explained throughout this section. 

During this pass of the analysis, 
we focused on the optimization of the signal jets selection in both resolved and merged regime 
during the R\&D phase of the analysis and introduced new criteria with respect to the early run-2 version of this analysis:

\begin{itemize}
  \item moving signal jets selection ($V \rightarrow qq$ decay products) from close-V algorithm to leading $p_T$ criteria; some studies are showed in appendix \ref{app:res_opt};
  \item moving to latest boson tagger configuration (3-variables instead of the previous 2-variables), details and references to the new tagger are put in section \ref{subsec:large-Rjet};
  \item moving to an inclusive merged CR instead of HighPurity/LowPurity (defined in Section \ref{subsubsec:merged_jets_selection}) CRs in order to take into account recommendation for boson tagger SFs, details are discussed in appendix \ref{app:merged_cr}.
\end{itemize}

The SM EW VV+jj MC samples have been used to check the sensitivity to our target signal process.

% move here after Oldrich comment
\input{src/event_selection/SummarySelections}
%
\input{src/event_selection/EventCleaning}
%
\input{src/event_selection/TriggerSelection}
%
\input{src/event_selection/EventPreSel}
%
\input{src/event_selection/LeptonsSelection}
%
\input{src/event_selection/VBSSelection}
%
\input{src/event_selection/SRSelection}
%
\input{src/event_selection/TopVetoSelection}
%
\input{src/event_selection/CRSelection}
%
\input{src/event_selection/CutFlows}
