%% Create a List of Abbreviations. The left column
%% is 1 inch wide and left-justified
\chapter{List of Abbreviations}

%% List of Abbreviations, edit as needed
\begin{symbollist*}
\item[2HDM] Two-Higgs Doublet Model.
\item[AK4] An anti-$k_t$ jet with $R = 0.4$.
\item[ALICE] A Large Ion Collider Experiment.
\item[AM] Associated Memory.
\item[AMB] Associated Memory Board.
\item[ATCA] Advanced Telecommunications Computing Architecture.
\item[ATLAS] A Toroidal LHC ApparatuS.
\item[AUX] Auxiliary Board.
\item[AXW] AUX Wrapper.
\item[BR] Branching Ratio.
\item[CA12] A Cambridge/Aachen jet with $R = 1.2$.
\item[CC] Clock Correction.
\item[CERN] European Organization for Nuclear Research.
\item[CL] Confidence Level.
\item[CMS] Compact Muon Solenoid.
\item[CP] Combined Performance.
\item[CR] Control Region.
\item[DF] Data Formatter.
\item[DFW] DF Wrapper.
\item[DRAM] Dynamic Random Access Memory.
\item[DSP] Digital Signal Processing Block.
\item[ECAL] Electromagnetic Calorimeter.
\item[ECR] Event Count Reset.
\item[EGM] Extended Gauge Model.
\item[EF] Event Filter.
\item[ELID] Extended Level 1 Identifier.
\item[EXP] Extrapolator.
\item[EXTF] Extrapolator / Track Fitter.
\item[FC] Flow Control.
\item[FCAL] Forward Calorimeter.
\item[FE] Front End.
\item[FF] Flip Flop.
\item[FIFO] First In First Out.
\item[FLIC] FTK Level-2 Interface Crate.
\item[FPGA] Field Programmable Gate Array.
\item[FSR] Final State Radiation
\item[fSSB] Final Second Stage Board.
\item[FTK] Fast TracKer.
\item[GTX] Gigabit Transceiver.
\item[ggF] gluon Fusion.
\item[HEP] High Energy Physics.
\item[HLT] High Level Trigger.
\item[HP] High Purity.
\item[HVT] Heavy Vector Triplet.
\item[HW] Hit Warrior.
\item[HXMPP] Hit Memory++.
\item[IBL] Insertable B Layer.
\item[ID] Inner Detector.
\item[IM] Input Mezzanine.
\item[ISR] Initial State Radiation.
\item[JVF] Jet Vertex Fraction.
\item[JER] Jet Energy Resolution.
\item[JES] Jet Energy Scale.
\item[KK] Kaluza-Klein.
\item[L1] Level 1 Hardware Trigger.
\item[L2] Level 2 Hardware Trigger.
\item[LAMB] Local Associated Memory Board.
\item[LDC] Link Destination Card.
\item[LED] Light Emitting Diode.
\item[LFSR] Linear Feedback Shift Register.
\item[LHC] Large Hadron Collider.
\item[LHCb] Large Hadron Collider beauty.
\item[LINAC2] Linear Accelerator 2.
\item[LP] Low Purity.
\item[LSC] Link Source Card.
\item[LUT] Look Up Table.
\item[MC] Monte Carlo.
\item[MET] Missing Transverse Energy.
\item[MIG] Memory Interface.
\item[ML] Maximum Likelihood.
\item[MS] Muon Spectrometer.
\item[NLO] Next to Leading Order.
\item[NNLO] Next to Next to Leading Order.
\item[PDF] Parton Distribution Function.
\item[PIX] Pixel Detector.
\item[PU] Processing Units.
\item[PS] Proton Synchrotron.
\item[pSSB] Preliminary Second Stage Board.
\item[QCD] Quantum Chromo Dynamics.
\item[QSFP] Quad Small Form-factor Pluggable.
\item[RAM] Read Access Memory.
\item[RLDRAM] Reduced Latency DRAM.
\item[ROD] Read Out Driver.
\item[ROI] Region of Interest.
\item[ROM] Read Only Memory.
\item[ROS] Read Out System.
\item[RS] Randall-Sundrum.
\item[RTM] Rear Transmission Module.
\item[RX] Receiver.
\item[SCT] Semiconductor Tracker.
\item[SE] Sync Engine.
\item[SF] Scale Factor.
\item[SFP] Small Form-factor Pluggable.
\item[SLink] Super Link.
\item[SM] Standard Model.
\item[SPS] Super Proton Synchrotron.
\item[SR] Signal Region.
\item[SSB] Second Stage Board.
\item[SSID] Super Strip Identifier.
\item[TDAQ] Trigger and Data Acquisition.
\item[TF] Track Fitter.
\item[TFW] Track Fitter Wrapper.
\item[TileCAL] Hadronic Calorimeter.
\item[TRT] Transition Radiation Tracker.
\item[TX] Transmitter.
\item[VBF] Vector Boson Fusion.
\item[VME] VERSA-Module Euro.
\item[VR] Validation Region.
\end{symbollist*}

%% Symbol defs
\def\met{\ensuremath{E_{\mathrm{T}}^{\mathrm{miss}}}}

%% Create a List of Symbols. The left column
%% is 0.7 inch wide and centered
%% Edit as needed

\chapter{List of Symbols}

\begin{symbollist}[0.7in]
    \item[$\ell$] lepton.
    \item[$e$] electron.
    \item[$\mu$] muon.
    \item[$\tau$] tau.
    \item[$\nu_{e}$] electron neutrino.
    \item[$\nu_{\mu}$] muon neutrino.
    \item[$\nu_{\tau}$] tau neutrino.
    \item[$q$] quark, also used for charge.
    \item[$u$] up quark.
    \item[$d$] down quark.
    \item[$s$] strange quark.
    \item[$c$] charm quark.
    \item[$b$] bottom quark.
    \item[$t$] top quark.
    \item[$g$] gluon.
    \item[$\gamma$] photon.
    \item[$W$] $W$ boson.
    \item[$Z$] $Z$ boson.
    \item[$H$] Higgs boson.
    \item[$V$] Vector boson.
    \item[$p$] proton.
    \item[$n$] neutron.
    \item[$G^*$] RS graviton.
    \item[$G_{KK}$] KK graviton.
    \item[$W'$] Heavy $W$ boson.
    \item[$Z'$] Heavy $Z$ boson.
    \item[$V'$] Heavy Vector Boson.
    \item[$E_T^{miss}$] Missing transverse energy.
    \item[$E_T$] Transverse energy.
    \item[$p_T$] Transverse momentum.
    \item[$\eta$] pseudo rapidity.
    \item[$\theta$] polar angle.
    \item[$\phi$] azimuthal angle.
    \item[$d_0$] the distance to the $z$-axis at the perigee point.
    \item[$z_0$] the $z$-coordinate at the perigee point.
    \item[$\phi_0$] the azimuthal angle at the perigee point.
    \item[$\chi^2$] statistic that measures how good the data fits the track.
    \item[$R$] distance in $\eta-\phi$ space.
    \item[$j$] small-$R$ jet.
    \item[$J$] large-$R$ jet.
    \item[$g_f$] fermion coupling.
    \item[$g_H$] Higgs and vector boson coupling.
    \item[$g_\ell$] lepton coupling.
    \item[$g_q$] quark coupling.
    \item[$\sigma$] cross section.
    \item[$m$] mass.
    \item[fb] femto barn $= 10^{-43}~\mathrm{m}^2$.
    \item[eV] electron Volt $= 1.602 \times 10^{-19}~\mathrm{J}$.
\end{symbollist}
